Initial Analysis

### 2020-07-15 Scripts/Initial_Analysis.Rmd
Changed cath trend categories to increasing constant and decreasing

Status_Per_Species <- Tresholded_T_Data %>% 
  left_join(Status_Data, 
            by =c("eez_name","taxon_key")
  ) %>%
  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
  group_by(taxon_key,status) %>% 
  summarise(value = length(unique(fishing_entity))) %>% 
  mutate(Categories = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
                             ifelse(status == "Max Exploited","Category B",
                                    ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
                             )
  )
  ) %>% 
  left_join(cc_vul) %>% 
  left_join(fish_vul) %>% 
  filter(status != "No Category",
         Categories != "No Category")

>>>>

Status_Per_Species <- Tresholded_T_Data %>% 
  left_join(Status_Data, 
            by =c("eez_name","taxon_key")
  ) %>%
  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
  group_by(taxon_key,status) %>% 
  summarise(value = length(unique(fishing_entity))) %>% 
  mutate(Categories = ifelse(status %in% c("Developing","Rebuilding"),"Increasing",
                             ifelse(status == "Max Exploited","Constant",
                                    ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Decreasing", "No Category")
                             )
  )
  ) %>% 
  left_join(cc_vul) %>% 
  left_join(fish_vul) %>% 
  filter(status != "No Category",
         Categories != "No Category")
